Dirac neutrino mass generation from Majorana messenger

### 2019-09-18 draft.tex

In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators. 
The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram. In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
We have showed that beyond the minimal model The new states required  may also lead to other phenomenological signals
at future hadron collider as well as lepton flavour violation experiments
We have illustrated our proposal by considering a specific
model, where simple numerical estimates allow us to show the effectiveness of the scheme regarding neutrino masses, DM and lepton flavor violating processes. Furthermore,.

>>>>

In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators. 
The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram. In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
We have showed that going beyond the minimal model other phenomenological signals
at future hadron collider as well as lepton flavour violation experiments
We have illustrated our proposal by considering a specific
model, where simple numerical estimates allow us to show the effectiveness of the scheme regarding neutrino masses, DM and lepton flavor violating processes. Furthermore,.
